\vspace{-1in}Identity signaling model progress

### 2020-03-31 reports/Progress.tex
created runners for invasion experiment, on to test this on cluster

>>>>

\section{Invasion experiments}

Here we run identical experiments, but vary the initial proportion of 
churlish receivers and covert receivers over $\{0.05, 0.5, 0.95\}$ for a total
of nine parameter combinations. One of these is a repeat of the previous
experiments, where both parameters are set to 0.5. Below are two figures.
The first is nine parameter settings where the density of covert signalers
is plotted in a heatmap (Figure~\ref{fig:invasion-signaling}). The second has 
heatmaps of the density of churlish receivers (Figure~\ref{fig:invasion-receiving}).

\input{invasion-figures.tex}
